Manuscript_Github_Pchabaudi_pir

### 2021-03-22 Manuscript_pirAnalysis_Github/Pchabaudi24h/Manuscript_Github_Pchabaudi_pir.Rmd
supp fig 9 only RMT

  cir_plot <- twentyfour_ct_comb%>% 
    filter(Geneid %in% cir_id) %>%
    melt(id.vars = 'Geneid', 
         variable.name = 'sample', 
         value.name = 'tpm') %>% 
    mutate(stage = gsub(sample, pattern = '_[[:digit:]]$', replacement = ''),
           transmission = str_split_fixed(sample, pattern = '_', n = 3)[,1],
           diff_count = str_split_fixed(sample, pattern = '_', n = 4)[,3],
           time = str_split_fixed(sample, pattern = '_', n = 3)[,2],
           subfam = cir_info$subfam[match(Geneid, cir_info$Geneid)],
           chapl_aapl = factor(cir_info$chapl_aapl_name[match(Geneid, 
                                                                    cir_info$Geneid)],
                               levels = sort(unique(cir_info$chapl_aapl_name[match(Geneid, 
                                                                                         cir_info$Geneid)])))) %>% 
    filter(!(time %in% c('sch', 
                         'Unknown')),
           !is.na(chapl_aapl) ) %>% 
    group_by(Geneid) %>% 
    # filter(
    #   # all(tpm < 100),
    #   #      any(tpm > 50)
    #   subfam == 'S7'
    #   ) %>% 
    arrange(desc(tpm))

  cir_plot_order <- cir_plot %>% 
    filter(time == '14h',
           transmission == 'SBP') %>% 
    arrange(desc(tpm))

@@

    y <- ggplot(
      data = cir_plot,
      mapping = aes(
        x = Geneid,
        fill = transmission,
        y = tpm
      )
    ) +
    stat_summary(fun.y = median, 
                 fun.ymin = median, 
                 fun.ymax = median,
                 geom = "bar", 
                 width = 0.75, 
                 size = 0.25, 
                 position = 'dodge') +
    geom_point(stat = 'identity', 
               position = position_dodge(width = 0.75),
               size = point_size) +
    scale_y_continuous(breaks = breaks,
                       limits = limits) +
      scale_fill_manual(values = c('skyblue','red')) +
      ylab('log(TPM +1)') +
    facet_grid(.~chapl_aapl, 
             scales = "free_x",
             space = "free_x") +
    theme_classic() +
    theme(
      axis.text.x = element_text(angle = 90,
                                 size = 5)
    ) +
    ggtitle(paste(unique(cir_plot$time)))

>>>>

cir_plot <- twentyfour_rMT %>% 
  filter(Geneid %in% cir_id) %>%
  melt(id.vars = 'Geneid', 
       variable.name = 'sample', 
       value.name = 'tpm') %>% 
  mutate(
    stage = gsub(sample, pattern = '_[[:digit:]]$', replacement = ''),
    diff_count = str_split_fixed(sample, pattern = '_', n = 4)[,2],
    time = str_split_fixed(sample, pattern = '_', n = 3)[,1],
    subfam = cir_clade_info$clade[match(Geneid, cir_clade_info$Geneid)],
    chapl_aapl = factor(cir_info$chapl_aapl_name[match(Geneid, 
                                                       cir_info$Geneid)],
                        levels = sort(unique(cir_info$chapl_aapl_name[match(Geneid, 
                                                                            cir_info$Geneid)])))) %>% 
  filter(!(time %in% c('sch', 
                       'Unknown')),
         !is.na(chapl_aapl) ) %>% 
  group_by(Geneid) %>% 
    arrange(desc(tpm))

@@

    y <- ggplot(
      data = cir_plot,
      mapping = aes(
        x = Geneid,
        y = tpm
      )
    ) +
    stat_summary(fun.y = median, 
                 fun.ymin = median, 
                 fun.ymax = median,
                 geom = "bar", 
                 width = 0.75, 
                 size = 0.25, 
                 position = 'dodge',
                 fill = 'lightblue') +
    geom_point(stat = 'identity', 
               position = position_dodge(width = 0.75),
               size = point_size) +
    scale_y_continuous(breaks = breaks,
                       limits = limits) +
      scale_fill_manual(values = c('skyblue','red')) +
      ylab('log(TPM +1)') +
    facet_grid(.~chapl_aapl, 
             scales = "free_x",
             space = "free_x") +
    theme_classic() +
    theme(
      axis.text.x = element_text(angle = 90,
                                 size = 5)
    ) +
    ggtitle(paste(unique(cir_plot$time)))
